Mining of Keystroke and Mouse Dynamics to Increase the Engagement of Students with Programming Assignments

### 2018-04-21 paper.tex
Check again new table and comments around it @mariosky

\begin{table}[h!tb]
\centering
\caption{Parameters used in the evolutionary algorithm for feature
  selection.}
\label{tab_ga}
    \begin{tabular}{ | l | l | }
      \hline
      Parameter & Value \\
      Population size & 700 \\
      Generations & 30 \\
      Selection & Tournament \\
      Tournament size & 25\% of population size \\
      Crossover & Uniform \\
      Crossover probability & 0.5 \\
      Mutation rate & $1 \over 39$ \\
      Minimum number of features & 5 \\
    \end{tabular}
  \end{table}

@@

Table \ref{tab_performance} shows the performance of each of the four
classifiers together
with the $\kappa$ coefficients. A 10-Fold cross validation was used.
The accuracies and $\kappa$ coefficients obtained are close to what is
usually obtained in fixed-text methods, for example, the results presented in
Epp, Lippold y Mandryk \cite{epp2011identifying}.
In a fixed-text method, subjects are asked to write specific texts.
The results obtained with this method are satisfactory, considering that
learners were writing a program, a task comparable with free-text writing,
where there is no restriction on what has to be written.
In the case of the $\kappa$ coefficients, it is
usual to see values below 0.2 in methods involving free-text. In this case, some
values of $\kappa$ were close to 0.5, is important to consider the values of $\kappa$
in these results because the class distribution is not uniformly distributed. As
it is observed in many works in affective recognition, decision trees normally
produce competitive accuracy. In this case the J-48 classifier obtained an
accuracy of 80.48\%, which is marginally better than the others, and an accepted $\kappa$
statistic for the kind of problem. The artificial neural network (ANN)
gives the highest
accuracy in the classification of frustration.

Table \ref{tab_perf_flow} shows the performance for the additional classifiers
evaluated specifically for the Flow/engaged affective state. The goal was to
increase the performance achieved earlier. Again a ten-
fold cross-validation was conducted. In this case, instead of using an
evolutionary algorithm to optimize feature selection, it was used for 
optimizing a weight vector. 
The feature-weight vector assigned a weight to each o the features. The
parameters used for the evolutionary optimization algorithm are the following:
Population size = 10, generations = 30, selection = tournament, tournament size = 0.25 (fraction of the population),  initialize probability = 0.5,  mutation
probability = 1/number of attributes,  crossover probability = 0.5. Parameters
used for the Random Forest algorithm: number of trees = 10, 
criterion = gain ratio, maximal depth = 20, 
confidence = 0.25, minimal gain = 0.1, minmail leaf size = 2.  The
parameters used for are the J48 are the following:  confidence = 0.79, minimal
leaf size=2. For the kNN algorithm, the value k = 4 was used. 
For gradient boosted
trees: number of trees = 20,  maximal depth = 5, minimum rows = 10, 
minimum split 
improvement = 0.0, number of bins = 20, 
learning rate = 0.1, sample rate = 1.0.  Bayes
Kernel: laplace correction = True, estimation mode = greedy, 
minimum bandwidth = 0.1, number of kernels = 10.  Finally for deep learning: activation = Rectifier, hidden layer sizes = [50, 50], epochs = 10.

>>>>

\begin{table}[h!tb]
\centering
\caption{Parameters used in the evolutionary algorithm for feature
  selection.}
\label{tab_ga}
    \begin{tabular}{ | l | l | }
      \hline
      Parameter & Value \\
      \hline
      Population size & 700 \\
      Generations & 30 \\
      Selection & Tournament \\
      Tournament size & population size / 4 \\
      Crossover & Uniform \\
      Crossover probability & 0.5 \\
      Mutation rate & $1 \over 39$ \\
      Minimum number of features & 5 \\
            \hline

    \end{tabular}
  \end{table}

@@

Table \ref{tab_performance} shows the performance of each of the four
classifiers together
with the $\kappa$ coefficients. A 10-Fold cross validation was used.
The accuracies and $\kappa$ coefficients obtained are close to what is
usually obtained in fixed-text methods, for example, the results presented in
Epp, Lippold y Mandryk \cite{epp2011identifying}.
In a fixed-text method, subjects are asked to write specific texts.
The results obtained with this method are satisfactory, considering that
learners were writing a program, a task comparable with free-text writing,
where there is no restriction on what has to be written.
In the case of the $\kappa$ coefficients, it is
usual to see values below 0.2 in methods involving free-text. In this case, some
values of $\kappa$ were close to 0.5, is important to consider the values of $\kappa$
in these results because the class distribution is not uniformly distributed. As
it is observed in many works in affective recognition, decision trees normally
produce competitive accuracy. In this case the J-48 classifier obtained an
accuracy of 80.48\%, which is marginally better than the others, and an accepted $\kappa$
statistic for the kind of problem. The artificial neural network (ANN)
gives the highest
accuracy in the classification of frustration.
%
\begin{table}[h!tb]
\centering
\caption{Parameters used in the evolutionary algorithm for feature
  weight optimization.}
\label{tab_ga_w}
    \begin{tabular}{ | l | l | }
      \hline
      Parameter & Value \\
        \hline
      Population size & 10 \\
      Generations & 30 \\
      Selection & Tournament \\
      Tournament size & population size / 4 \\
      Crossover & Uniform \\
      Crossover probability & 0.5 \\
      Mutation rate & $1 \over 39$ \\
      Minimum number of features & 5 \\
        \hline
    \end{tabular}
  \end{table}
% 
\begin{table*}[!t]
\centering
\caption{Parameters used for the different classification algorithms }
\label{tab_params_ml}
\label{tab_perf_flow}
    \begin{tabular}{ | l | l |  }

      Algorithm & Parameters \\
      \hline
    \end{tabular}
  \end{table}

Table \ref{tab_perf_flow} shows the performance for the additional classifiers
evaluated specifically for the Flow/engaged affective state. The goal was to
increase the performance achieved earlier. Again a ten-
fold cross-validation was conducted. In this case, instead of using an
evolutionary algorithm to optimize feature selection, it was used for 
optimizing a weight vector. 
      The feature-weight vector assigned a weight to each one of the
      features, and the parameters that have been used in the
      evolutionary algorithm are shown in Table \ref{tab_ga_w}.
      % The
% parameters used for the evolutionary optimization algorithm are the following:
% Population size = 10, generations = 30, selection = tournament, tournament size = 0.25 (fraction of the population),  initialize probability = 0.5,  mutation
%       probability = 1/number of attributes,  crossover probability =
%       0.5.
      % Please Mario check these parameters and how they have put to
      % the table; I don't know what's the "initialization
      % probability" - JJ

      Parameters
used for the Random Forest algorithm: number of trees = 10, 
criterion = gain ratio, maximal depth = 20, 
confidence = 0.25, minimal gain = 0.1, minmail leaf size = 2.  The
parameters used for are the J48 are the following:  confidence = 0.79, minimal
leaf size=2. For the kNN algorithm, the value k = 4 was used. 
For gradient boosted
trees: number of trees = 20,  maximal depth = 5, minimum rows = 10, 
minimum split 
improvement = 0.0, number of bins = 20, 
learning rate = 0.1, sample rate = 1.0.  Bayes
Kernel: laplace correction = True, estimation mode = greedy, 
minimum bandwidth = 0.1, number of kernels = 10.  Finally for deep learning: activation = Rectifier, hidden layer sizes = [50, 50], epochs = 10.
